{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-05 wacv_for_review.tex

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target as shown in Figure~\ref{fig:Filters}.

@@

\textbf{{\it E}nKCF with Hand-Crafted Features}

{\it Burak: You need to rewrite this section and the section about
  deep features! Try to make it concise with short sentences! It is
  even hard for me to read this section and catch the main idea.}

We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.

In particular, the translation filter, $R_{t}^{L}$, employs
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
compensate for the noisier fHoG features due to the large background area considered 
by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

  {\it YoungWoo : The weakness is the more background you include the noisier
  HoG features become.}
On the other hand, the color features is not assigned to the small area translation 
filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
since the ROI is resized to a lower template resolution (64 x n) than the translation filters. This leads to 
less discriminative shape features as in Figure~\ref{fig:Filters}.c. The $R_{s}$ estimates
the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
due to two major reasons: (1) zero padding size and (2) integration of color features.
This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, fluctuating run-time performances among KCFs are avoided which is
desired in embedded systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance. {\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}
  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} As
explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features as shown in Figure~\ref{fig:Filters}.  
With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

%\textbf{Features Selections} We used different features for each of
%three KCFs as each of them has different goals to accomplish. In
%particular, the translation filter, $R_{t}^{L}$, uses both the fast
%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
%and color-naming \cite{van2009learning} features to more effectively
%learn the background around the target as shown in figure~\ref{fig:Filters}. 
%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
%translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
To further improve the performance, we employed deeper features in the scale filter since it has zero
padding around the target.

>>>>

The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
first filter, $R_{t}^{S}$, focuses on learning the target area and its
background, \textit{target}+\textit{small background} for addressing a
marginal translation by a target, the second filter, $R_{s}$, focuses
entirely on learning the target's scale, \textit{target-only}, and the
last filter, $R_{t}^{L}$, focuses on the target area and its
background, at least twice, bigger than that of the first filter,
$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
  E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target {\it Burak: We only explained two kinds of
  filters: translation and scale filter. But we do have two filters
  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
  the sentence about translation filter with details.} 
  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
  translation filter needs background whereas the scale filter does not.}
Figure \ref{fig:Filters} shows examples of three filters.

@@

{\it Burak: This section does NOT connect to the previous section.}

{\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
placed them after the Kernelized Correlation Filter section. }

\textbf{{\it E}nKCF with Hand-Crafted Features} 
We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters} (b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noises the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
because the translation filter, {\it target + small background}, does
not contain much of the background area around the target. Figure
\ref{fig:Filters} (a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters} (c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
due to two major reasons: (1) zero padding size and (2) integration of color features.
This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
addition to hand-crafted features, we explore deep features to boost
tracking performance.

{\it Burak: Did EnKCF w/ deep features really
  improve the performance -- the performance tested on the same data?
  or did you just compare the performance numbers?}

{\it YoungWoo :
  EnkCF with deep features improved the performance on the same set of
  data.}

{\it Burak: If EnKCF w/ deep features improved the performance of
  EnKCF on the same set of data, why didn't you plot their curves
  together? And if this is true, we'll have to revise the abstract and
  introduction as well!}

  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}

This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
devised to make {\it E}nKCF run on high-end embedded systems with GPUs
installed.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} 
{\it Burak: Does what this section explains still hold good? If what
  this section explains still makes sense, the translation filter,
  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
  this section.}

  {\it YoungWoo : I did not understand what $R_{t}^{L}$ has to do with 
  particle filter}

As explained earlier, the {\it E}nKCF updates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs of the {\it E}nKCF. In
particular, we use a particle filter to estimate the target's image
coordinate based on the {\it E}nKCF's outputs. A particle filter is a
sequential Monte Carlo method that uses a finite number of particles
or samples to estimate the posterior probability density of a state of
the system \cite{thrun2005probabilistic}. In this study, the state
represents a target's pixel coordinates and its motion. In particular,
the state of the particle filter, $X_t$, is represented by $\lbrace x,
y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
along the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
size of the window as that of a confidence map. Alternatively one can
also use the Euclidean distance of particles to the location of
maximum response of the confidence map.
\begin{comment}
We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.
\end{comment}

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features as shown in Figure \ref{fig:Filters}.  
With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Also, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets. Finally, we evaluate the Deep{\it E}nKCF, 
{\it E}nKCF with deep features, on the UAV123 dataset to observe how much gain
we can achieve over hand-crafted features.

@@

%\textbf{Features Selections} We used different features for each of
%three KCFs as each of them has different goals to accomplish. In
%particular, the translation filter, $R_{t}^{L}$, uses both the fast
%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
%and color-naming \cite{van2009learning} features to more effectively
%learn the background around the target as shown in Figure \ref{fig:Filters}. 
%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
%translation filter, $R_{t}^{S}$, worked well when it used fHoG
%features only; the scale filter, $R_{s}$ did when it used both fHoG
%and color features.

@@

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used fHoG and color-naming features in an
efficient way in the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. Following the recent trend, we hypothesize 
that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
dataset. Utilizing pre-trained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. However, as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in Figure \ref{fig:Filters_CNN}.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
We further improved the performance by employing deeper features in the scale filter since it has zero
padding around the target.
